### 2021-06-12 code/manuscript.Rmd
clean-up preprocessing

# Re-run preprocessing and/or model fitting?
rerun_preprocessing <- TRUE
rerun_model_fitting <- FALSE

@@

  # Do the actual preprocessing
  tibble(fname_vhdr, fname_log, subject_id) %>%
    pwalk(
      pp$preprocess,
      output_dir = "data/preprocessed",
      eog_names = c("HEOG", "VEOG"),
      eog_anodes = c("F9", "Auge_u"),
      eog_cathodes = c("F10", "Fp1"),
      montage_kind = "easycap-M1",
      ica_components = as.integer(15),
      ica_method = "fastica",
      ica_seed = as.integer(1234),
      hipass = 0.1,
      lowpass = 30,
      event_id = dict(match = as.integer(221), mismatch = as.integer(222)),
      tmin = -0.5,
      tmax = 1.489,
      baseline = tuple(-0.2, 0),
      reject = dict(eeg = 200e-6),
      erp_components = erp_components,
      average_by = c("part", "condition", "subject_id"),
      tfr_equalize = "condition == ['Informed', 'Naive']",
      tfr_resample = py_none(),
      tfr_freqs = tfr_freqs,
      tfr_cycles = tfr_cycles,
      tfr_crop = tuple(-0.2, 0.8)
    )

@@

# Scaling of power in all plots
limits_power <- c(0, 2)

>>>>

# Re-run preprocessing and/or model fitting?
rerun_preprocessing <- TRUE
rerun_model_fitting <- TRUE

@@

  # Do the actual preprocessing
  tibble(fname_vhdr, fname_log, subject_id) %>%
    pwalk(
      pp$preprocess,
      output_dir = "data/preprocessed",
      eog_names = c("HEOG", "VEOG"),
      eog_anodes = c("F9", "Auge_u"),
      eog_cathodes = c("F10", "Fp1"),
      montage_kind = "easycap-M1",
      ica_components = as.integer(15),
      ica_method = "fastica",
      ica_seed = as.integer(1234),
      hipass = 0.1,
      lowpass = 30,
      event_id = dict(match = as.integer(221), mismatch = as.integer(222)),
      tmin = -0.5,
      tmax = 1.489,
      baseline = tuple(-0.2, 0),
      reject = dict(eeg = 200e-6),
      erp_components = erp_components,
      average_by = c("part", "condition", "subject_id"),
      tfr_baseline = tuple(-0.3, -0.1),
      tfr_equalize = "condition == ['Informed', 'Naive']",
      tfr_resample = py_none(),
      tfr_freqs = tfr_freqs,
      tfr_cycles = tfr_cycles,
      tfr_crop = tuple(-0.2, 0.8)
    )

@@

# Scaling of power in all plots
limits_power <- c(0, 0.5)
